Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-12-24 journal-draft/ettdoc_JG.tex
polish the tabel of notations, polish the introduction of \delta

We next focus on a single CR cluster. 
A cluster $C$ is a set of secondary nodes in an area, and there is a set of common channels which are available to each node belonging to the cluster.
One of the nodes belonging to the cluster is furthermore the cluster head $h(C)$.
The cluster head is able to communicate with any cluster member directly.
%Our scheme enables the cluster heads to be selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
%C1-4
%$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
%For any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
The number of nodes belonging to $C$ is denoted by $|C|$.
When the cluster head of a cluster is $i$, we denote that cluster by $C(i)$.
$K(C)$ denotes the set of CCs of all nodes in cluster $C$, i.e. $ K(C) = \bigcap_{i\in C} K_i$.
%Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
Table~\ref{tab1} summarizes all parameters and their assumed relevance in our system model.
\begin{table}[h!]
\caption{Notations}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
Symbol & Description \\
\midrule
$\mathcal{N}$  & set of CR users in a CRN\\
$N$ & number of CR users in a CRN, $N=|\mathcal{N}|$\\
$\mathcal{K}$	& set of licensed channels\\
$k(i)$ & the working channel of user $i$\\
$\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
$C(i)$ & a cluster whose cluster head is $i$  \\
$K_i$   & the set of available channels at CR node $i$  \\
$K(C(i))$   & the set of available CCs of cluster $C(i)$ \\
%$h(C)$ & cluster head of a cluster $C$\\
$h(C)$ & the cluster head of a cluster C\\
%$\text{CH}$ & cluster head\\
%$\text{CH}$ & cluster head\\
$\delta$ & the desired cluster size\\
$S_i$ & a set of claiming clusters, each of which \\
& includes debatable node $i$ after phase I\\
$f(C)$ & the number of CCs of a cluster $C$ in the\\ 
& problem description\\
% $\mathcal{G}$ & a collection of some possible clusters in $\mathcal{N}$\\
 $\mathcal{S}$ & the collection of all the possible clusters in $\mathcal{N}$\\
 $C_i$  & the $i$-th cluster in $\mathcal{S}$ \\
 $|C_i|$ & the size of the cluster $C_i$\\
 $|K(C_i)|$ & the number of CCs of cluster $C_i$\\
 $M$ & the cardinality of set $\mathcal{S}$ which contains all\\ 
 & the possible clusters (Sec.~\ref{centralized_solution})\\
 $p(C_i)$ & the weight with respect to cluster $C_i$ (Sec.~\ref{centralized_solution}) \\
 $d_i$  & individual connectivity degree of CR node $i$\\
$g_i$  & neighborhood connectivity degree of CR node $i$\\
  $n$ & the number of debatable nodes\\
 $m$ & the number of claiming cluster heads\\
 $J$ & the new value of $d_i$ for the CR node after it\\
 & becomes a cluster member (Sec.~\ref{ross})\\
% $e$ & cost function in the formulated game (Sec.~\ref{clustering:phaseII:game})\\
\bottomrule
\end{tabular}
\end{table}

@@

As to the objective function, the sum of the first term in the bracket over all clusters in $\mathcal{S}$ is the sum of CCs of the clusters which constitute the CRN.
In the second term in the bracket, we propose $p(C_i)$ which is a size-related weight for cluster $C_i, i\in{1,\cdots, M}$.
$p(C_i)$ is positively related with the difference between $C_i$'s size and the desired size $\delta$.
When $x_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, the second item is negative, which contradicts the direction of the optimization.
Thus the second item discourages the appearance the clusters whose sizes deviate from the desired cluster size $\delta$.
The weight $p(C_i)$ with respect to different cluster sizes is as follows,

$$
p(C_i) = \left\{ \begin{array}{rl}
0 &\mbox{ if $|C_i|=\delta$} \\
\rho(1) &\mbox{if $|C_i|=\delta \pm 1$ } \\
\rho(2) &\mbox{if $|C_i|=\delta \pm 2$} \\
\vdots\\
\rho(\sigma) &\mbox{if $|C_i|=\delta \pm \sigma$} \\
\end{array} \right.
$$
where $\rho$ is an increasing function and there is $ 0 < \rho(1)< \rho(2) < \cdots < \rho_(\sigma)$.
Note that here we adopt the desired cluster size in stead of the range for cluster sizes which is described in Definition~\ref{problem}.
Because in implementation, we usually need a large range to guarantee a feasible result for the optimization problem.
By adopting the desired size and the cost for deviating from it, we actually set a large range of cluster sizes and meanwhile a better control of the resulted sizes. 
Also to guarantee the feasibility of the problem, we allow the singleton cluster to contribute the objective function.

>>>>

We next focus on a single CR cluster. 
A cluster $C$ is a set of secondary nodes in an area, and there is a set of common channels which are available to each node belonging to the cluster.
One of the nodes belonging to the cluster is furthermore the cluster head $h(C)$.
The cluster head is able to communicate with any cluster member directly.
%Our scheme enables the cluster heads to be selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
%C1-4
%$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
%For any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
The number of nodes belonging to $C$ is denoted by $|C|$.
When the cluster head of a cluster is $i$, we denote that cluster by $C(i)$.
$K(C)$ denotes the set of CCs of all nodes in cluster $C$, i.e. $ K(C) = \bigcap_{i\in C} K_i$.
%Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
Table~\ref{tab1} summarizes all parameters and their assumed relevance in our system model. 
The usage scope is also provided when they are not used throughout the paper.
\begin{table}[h!]
\caption{Notations}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
Symbol & Description \\
\midrule
$\mathcal{N}$  & set of CR users in a CRN\\
$N$ & number of CR users in a CRN, $N=|\mathcal{N}|$\\
$\mathcal{K}$	& set of licensed channels\\
%$k(i)$ & the working channel of user $i$\\
$\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
$C(i)$ & a cluster whose cluster head is $i$  \\
$K_i$   & the set of available channels at CR node $i$  \\
$K(C(i))$   & the set of available CCs of cluster $C(i)$ \\
%$h(C)$ & cluster head of a cluster $C$\\
$h(C)$ & the cluster head of a cluster C\\
%$\text{CH}$ & cluster head\\
%$\text{CH}$ & cluster head\\
$\delta$ & the desired cluster size\\
$S_i$ & a set of claiming clusters, each of which \\
& includes debatable node $i$ after phase I\\
$f(C)$ & the number of CCs of a cluster $C$ in the\\ 
& problem description (Sec.~\ref{problem})\\
% $\mathcal{G}$ & a collection of some possible clusters in $\mathcal{N}$\\
 $\mathcal{S}$ & the collection of all the possible clusters \\
 & in $\mathcal{N}$ (Sec.~\ref{centralized_solution})\\
 $M$ & the cardinality of $\mathcal{S}$ (Sec.~\ref{centralized_solution})\\
 $C_i$  & the $i$-th cluster in $\mathcal{S}$ (Sec.~\ref{centralized_solution})\\
 %$|C_i|$ & the size of the cluster $C_i$\\
 %$|K(C_i)|$ & the number of CCs of cluster $C_i$\\
 $p(C_i)$ & the weight with respect to cluster $C_i$ (Sec.~\ref{centralized_solution}) \\
 $d_i$  & individual connectivity degree of CR node $i$\\
$g_i$  & neighborhood connectivity degree of CR node $i$\\
  $n$ & the number of debatable nodes\\
 $m$ & the number of claiming cluster heads\\
 $J$ & the new value of $d_i$ for the CR node after it\\
 & becomes a cluster member (Sec.~\ref{ross})\\
% $e$ & cost function in the formulated game (Sec.~\ref{clustering:phaseII:game})\\
\bottomrule
\end{tabular}
\end{table}

@@

As to the objective function, the sum of the first term in the bracket over all clusters in $\mathcal{S}$ is the sum of CCs of the clusters which constitute the CRN.
For the second term in the bracket, we propose $p(C_i)$ which is a size-related weight for cluster $C_i, i\in{1,\cdots, M}$.
$p(C_i)$ is positively related with the difference between $C_i$'s size and the desired size $\delta$.
When $x_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, the second item is negative, which contradicts the direction of the optimization.
Thus the second item discourages the appearance the clusters whose sizes deviate from the desired cluster size $\delta$.
The weight $p(C_i)$ with respect to different cluster sizes is as follows,

$$
p(C_i) = \left\{ \begin{array}{rl}
0 &\mbox{ if $|C_i|=\delta$} \\
\rho(1) &\mbox{if $|C_i|=\delta \pm 1$ } \\
\rho(2) &\mbox{if $|C_i|=\delta \pm 2$} \\
\vdots\\
\rho(\sigma) &\mbox{if $|C_i|=\delta \pm \sigma$} \\
\end{array} \right.
$$
where $\rho$ is an increasing function and there is $ 0 < \rho(1)< \rho(2) < \cdots < \rho_(\sigma)$.
Note that here we adopt the desired cluster size in stead of the upper and lower bounds for cluster sizes which is described in Definition~\ref{problem}.
%Because in implementation, we usually need a large range to guarantee a feasible result for the optimization problem.
With $\delta$ and the deviation from it, we actually set a large range of cluster sizes, which guarantees the feasibility of the problem as we allow the singleton cluster to appear, meanwhile a better control of the resulted sizes by setting weights for the formed clusters based on their deviations from the desired size.
%Also to guarantee the feasibility of the problem, we allow the singleton cluster to contribute the objective function.
